\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}

### 2023-02-03 latex/supplementary.tex

\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k+1  } \displaystyle e^{-\beta f(j-1)}

@@

By construction, the candidate stationary distribution given by Eq. \ref{Eq:stationary-dist-symm-2-stgs-state} and Eq. \ref{Eq:stationary-dist-normalization-symm-2-stgs-state} is a probability distribution since it satisfies the condition in Eq. \ref{Eq:normalizationcondition} and for any state $\abf'$, $\ubf_{\abf'}$ is between 0 and 1.  Moreover, since $\beta$ is finite, the transition matrix of the process $\T$ is primitive and therefore, it will have a unique stationary distribution. To show that the candidate stationary distribution is the unique stationary distribution, we need to check if for this process, $\ubf \T= \ubf$. That is, the Eq. \ref{Eq:transition-in-proof} must hold. We re-introduce some notations that we will use in this proof: 

@@

\\ \noindent Where, the function $\mathit{sign}(.)$ is  defined in Eq. \ref{Eq:sign-function} and$f(j)$ is the difference in payoffs between playing $\D$ and $\C$ when there are $j$ co-players playing $\C$. The term $N_k$ is the number of co-players of $k$ that play $\C$ in state $\abf_\C$. That is,

@@

N_k := \sum_{j \neq k} \alpha(\abf^l)

@@

&=  \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \left( \prod_{j=1}^{\sum_{j \neq k} \alpha(\abf^l)}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ \sum_{j \neq k} \abf^l)}

@@

Between the steps, Eq. \ref{Eq:step-single-product} and \ref{Eq:step-product-broken}, we took out one term from the product that is present in our candidate distribution. This term accounts for the $k^{th}$ players action in the state $(\bar{\abf}^k, \abf^{-k})$. For simplicity, we replace $\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})}$ with just $\T$ in the next steps and also denote the number of co-players of $k$ that play $\C$ in the state $\abf$ as $N_k$. 
\noindent We continue the simplification of Eq. \ref{Eq:step-product-broken} in the later steps by introducing terms that cancel each other. \\[10pt]

@@

\\ \noindent The newly introduced term in Eq. \ref{Eq:new-cancelable-term-introduced} can be taken inside the product. Note that this term is 0 if the $k^{th}$ player plays $\D$ in the state $\abf$. When this term is taken inside the product bracket, products of exponent $e^{-\beta f(j-1)}$ can be performed where $j$ ranges from $1$ to the number of cooperators in state $\abf$, $\mathcal{C}(\abf)$. This product is then the stationary distribution probability $\ubf_\abf$. That is, 

@@

\begin{proof}
\textbf{Proof of Corollary} \ref{Lemma: Symmetric-2-stg} \\ \\

\end{proof}
\newpage
\section*{Supplementary References}
\bibliographystyle{unsrt}
\bibliography{bibliography.bib }
\end{document}

>>>>

\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}

@@

By construction, the candidate stationary distribution given by Eq. \ref{Eq:stationary-dist-symm-2-stgs-state} and Eq. \ref{Eq:stationary-dist-normalization-symm-2-stgs-state} is a probability distribution since it satisfies the condition in Eq. \ref{Eq:normalizationcondition} and for any state $\abf'$, $\ubf_{\abf'}$ is between 0 and 1.  Moreover, since $\beta$ is finite, the transition matrix of the process $\T$ is primitive and therefore, it will have a unique stationary distribution. To show that the candidate stationary distribution is the unique stationary distribution, we need to check if for this process, $\ubf \T= \ubf$. That is, the condition in Eq. \ref{Eq:transition-in-proof} must hold for all states $\abf$. We re-introduce some notations that we will use in this proof: 

@@

\\ \noindent Where, the function $\mathit{sign}(.)$ is  defined as in Eq. \ref{Eq:sign-function} and$f(j)$ is the difference in payoffs between playing $\D$ and $\C$ when there are $j$ co-players playing $\C$. The term $N_k$ is the number of co-players of $k$ that play $\C$ in state $\abf$. That is,

@@

N_k := \sum_{j \neq k} \alpha(\abf^j)

@@

&=  \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k}

@@

Between the steps, Eq. \ref{Eq:step-single-product} and \ref{Eq:step-product-broken}, we took out one term from the product that is present in our candidate distribution. This term accounts for the $k^{th}$ players action in the neighbouring state $(\bar{\abf}^k, \abf^{-k})$ of $\abf$. For simplicity, we replace $\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})}$ with just $\T$ in the next steps. We continue the simplification of Eq. \ref{Eq:step-product-broken} in the later steps by introducing terms that cancel each other. \\[10pt]

@@

\\ \noindent The newly introduced term in Eq. \ref{Eq:new-cancelable-term-introduced} can be taken inside the product. Note that this term is 0 if the $k^{th}$ player plays $\D$ in the state $\abf$. When this term is taken inside the product bracket, products of exponent $e^{-\beta f(j-1)}$ can be performed for $j$ ranging from $1$ to the number of cooperators in state $\abf$, $\mathcal{C}(\abf)$. This product is then the stationary distribution probability $\ubf_\abf$. That is, 

@@

\textbf{Proof of Corollary} \ref{Lemma: Symmetric-2-stg} \\ \\
To show this result we count how many states are identical to a state $\abf \in \{\C,\D\}^N$ in a symmetric game. When players are symmetric in a two-strategy game, states can be enumerated by counting the number of $\C$ players in that state. This can also be confirmed by the expression of the stationary distribution in Eq. \ref{Eq:stationary-dist-symm-2-stgs-state}. Two distinct states $\abf, \abf'$ having the same number of cooperators (i.e., $\mathcal{C}(\abf') = \mathcal{C}(\abf)$), have the same stationary distribution probability (i.e., $\ubf_{\abf'} = \ubf_{\abf}$).
\\ \\ 
\noindent In a game with $N$ players, there can be $k$ players playing $\C$ in exactly $N \choose k$ ways. As argued before, all of these states are identical and are also equiprobable in the stationary distribution. Therefore, the stationary distribution probability of having $k$, $\C$ players, $\ubf_{k}$, is,
\ubf_{k} = \sum_{\forall \abf,  \mathcal{C(\abf)} = k} \ubf_\abf = \frac{1}{\Gamma} {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)} \\[10pt]
\noindent Where the normalization factor $\Gamma$ can also be simplified as: 
\Gamma = \sum_{k=0}^N {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)}
\section*{Supplementary References}
\bibliographystyle{unsrt}
\bibliography{bibliography.bib }
\end{document}
